Fossil-calibrated supermatrix phylogeny of Onagraceae: patterns of floral and chromosome evolution

### 2014-05-06 manuscript.tex
revised methods

\title{Fossil-calibrated phylogeny of Onagraceae: patterns of floral and chromosome evolution}

@@

I downloaded all available DNA sequences from GenBank release 200 PLN division and
performed an exhaustive all-by-all BLASTn \citep{blast} comparison for sequences in Onagraceae
and Lythraceae.
Using a BLASTn e-value of $1.0 \times 10^{-10}$ threshold and a sequence length
percent similarity cutoff of 0.5,
I constructed clusters of putative homologs using a single-linkage hierarchical clustering algorithm.
Subspecies names were removed from all sequences, and all but one sequence of each species was pruned from each cluster.
Clusters that were not phylogenetically informative ($< 4$ taxa) were discarded,
and each cluster was aligned using MUSCLE \citep{edgar2004muscle}. 
The alignments were concatenated by species, and any species that was not present in at least
two clusters was removed from the supermatrix.
Code written to assemble the supermatrix is available as the Python module 
SUMAC \citep[\url{https://github.com/wf8/sumac}]{sumac}, and can be used to assemble
supermatrices for other taxonomic groups recognized in GenBank.

>>>>

\title{Fossil-calibrated supermatrix phylogeny of Onagraceae: patterns of floral and chromosome evolution}

@@

Lythraceae was selected to use as an outgroup since previous molecular phylogenetic analyses
place it sister to Onagraceae \citep{conti1997, Sytsma2004}.
I downloaded all DNA sequences from GenBank release 200 PLN division and
performed an exhaustive all-by-all BLASTn \citep{blast} comparison of sequences in Onagraceae
and Lythraceae.
Using a BLASTn e-value of $1.0 \times 10^{-10}$ threshold and a sequence length
percent similarity cutoff of 0.5,
I constructed clusters of putative homologs using a single-linkage hierarchical clustering algorithm.
Subspecies names were removed from all sequences, and all but one sequence of each species was pruned from each cluster.
Clusters that were not phylogenetically informative ($< 4$ taxa) were discarded,
and each cluster was aligned using MUSCLE \citep{edgar2004muscle}. 
The alignments were concatenated by species, and any species that was not present in at least
two clusters was removed from the supermatrix.
The program written to data-mine GenBank and assemble the supermatrix 
is available as the open source Python module 
SUMAC \citep{sumac}.
SUMAC can be used to assemble
supermatrices for any taxonomic group recognized in GenBank, 
and is optimized to run on multicore processors and clusters by utilizing multiple parallel processes.
